### 2021-04-14 paper.Rmd
Comment about Figure 3, color description to change (dark2 palette)

>>>>

<!-- FIGURE 3, I think you are using Dark2 palette but in the figure caption you mention green and brown, I'm not colorblind but I check the palette description and the color is #D95F02 (https://www.colorhexa.com/d95f02) color description: Vivid orange. If this is correct, you should  replace  "brown" by orange in  Figure 3  caption and in  Figure 3 comments in page 4 (two brown each)-->
